Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-03-03 VegOzone.tex
Use final figures

\graphicspath{{pictures/}}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{svanhovd_researchstation}\\
  \includegraphics[width=8.3cm]{IMG_7739.JPG}  
  \caption{NIBIO Environment Centre Svanhovd close by the settlement of Svanvik, Norway. (a) Atmospheric monitoring site and ozone garden have been marked. Aerial photography \copyright Norges Kartverk; (b) Clover in the Svanhovd ozone garden. The plants had to be secured against herbivores with a wire-mesh fence. The plants shown are approximately $6-12\,\unit{cm}$ in height.}
  \label{fig:svanhovd_research_station}
\end{figure}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{data_svanvik_2018_2019}
  \caption{Observational data from atmospheric monitoring at Svanhovd in 2018/19. The hatched areas indicate missing ozone monitoring data. (a) Hourly averaged ozone concentration; (b) hourly averaged temperature; (c) daily accumulated precipitation; (d) hourly averaged global irradiance.}
  \label{fig:data_svanvik_2018_2019}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{station_map_fennoscandia}
  \caption{Cap of the North. Locations of past and present ozone observation sites in northern Fennoscandia used within this study. For more details see Tab.~\ref{tab:ebas_obs}. The same color coding for each station as displayed herein will be used in all following figures.}
  \label{fig:station_map_fennoscandia}
\end{figure}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}). Data taken from EBAS. The hatched areas indicate time periods with insufficient quality control \citep{NILU2003}.}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{climatediagram}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2012) downloaded from LandbruksMeteorologiske Tjeneste. Monthly averaged temperatures (red line) are displayed with standard error of mean as error band. Averaged monthly accumulated precipitation (blue bars) is shown with standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_spline}
  \caption{Derivation of ozone climatologies. Density distributions are shown together with multi-annual mean of daily ozone concentrations \chem{[O_3]}. Splines have been fitted though daily mean \chem{[O_3]}. The climatology of daily mean ozone is shown together with $1\,\sigma$ standard deviation and standard error of the mean. Since \chem{[O_3]} are strongly correlated for sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN) (see Fig.~\ref{fig:density_distribution}), data of these have been averaged together to derive a climatology for northern Fennoscandia. (a) Northern Fennoscandia; (b) Svanvik.}
  \label{fig:ozone_climatology_fenoscandic_obs_spline}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_climatologies_portrait}
  \caption{Comparison of climatologies derived from observational data (EBAS) with various ozone reanalysis products: (a) ECMWF: MACC reanalysis; (b) ECMWF: CAMS reanalysis; (c) Copernicus: Regional model reanalysis ensemble mean. As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays an erroneous seasonal cycle. The CAMS reanalysis matches better but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia, though the modeled ozone concentrations are slightly too low.}
  \label{fig:ozone_climatologies}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{temperature_signific_1}
  \caption{Temperature anomalies at Svanvik. Percentage of days warmer/colder than $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average, especially May and July. The summer of 2019 was fairly average but significantly warmer than average in April and colder in July/August.}
  \label{fig:plot_temperature_anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{precipitation_signific_1}
  \caption{Precipitation anomalies at Svanvik. Percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Summer was significantly dry only in 2018, while fall was significantly dry in both years.}
  \label{fig:plot_precipitation_anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{global_rad_signific_1}
  \caption{Global irradiance anomalies at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 had significantly less than normal irradiance in April/May and more in June.}
  \label{fig:global_rad_signific}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{ozone_signific_1}
  \caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details). In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  \label{fig:ozone_signific}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  \includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{javis_func_opt_mean.pdf}
  \caption{Proposed metric to test bespoke response functions.}
  \label{fig:javis_func_opt_mean}
\end{figure}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{do3se_results_pod_v3_Birch}\\
  \includegraphics[width=8.3cm]{do3se_results_pod_v3_Spruce}\\
  \includegraphics[width=8.3cm]{do3se_results_pod_v3_Grassland}
  \caption{Comprehensive comparison of $\mathrm{DO_3SE}$ modeling results with default parameterization from mapping manual (MM)and bespoke parameters for Svanhovd. $\mathrm{POD_1}$ is shown for the different temperature (MM, boreal, cold) and light threshold (MM, PPFD0.8, PPFD1.2) parameterizations at the end of the MM GS (lighter colors and dotted lines) and a derived bespoke GS. (a) Birch; (b) Norway spruce; (c) Perennial grassland.}
  \label{fig:pody_rel}
\end{figure}

@@

%\videosupplement{TEXT} %% use this section when having video supplements available

@@

\appendixfigures  %% needs to be added in front of appendix figures
\begin{figure*}[t]
  \includegraphics[width=12cm]{global_rad_clim}
  \caption{Observed global irradiance at Svanvik. (a) Climatology (hourly maxima, mean, and minima); deviation from climatology (b) 2018; (c) 2019. The cyan lines indicate the $1\,\sigma$ level derived from climatology.}
  \label{fig:global_rad_clim}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{density_distribution}
  \caption{Probability densities and correlation coefficient for \chem{[O_3]} between different sites in northern Fennoscandia. Jergul/Karasjok is well correlated with Esrange, and Pallas. Svanvik displays highest correlation with Pallas. (a) Jergul/Karasjok--Esrange; (b) Jergul/Karasjok--Pallas; (c) Svanvik--Esrange; (d) Svanvik--Pallas.}
  \label{fig:density_distribution}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{ozone_reconstruction_2018_07}
  \caption{Reconstruction of missing \chem{[O_3]} observation data at Svanvik in July 2018 based on derived hourly climatologies of northern Fennoscandia, Svanvik, and data Pallas. (a) Time series; (b) anomalies; (c) reconstruction.}
  \label{fig:ozone_reconstruction_2018_07}
\end{figure*}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{modis_Psn}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (doy) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure*}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{javis_funcs_temp_hist_evergreen}\\
  \includegraphics[width=8.3cm]{javis_funcs_rad_hist_evergreen}
\caption{Construction of bespoke response functions for Norway spruce. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_spruce}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=8.3cm]{javis_funcs_temp_hist_birch}\\
  \includegraphics[width=8.3cm]{javis_funcs_rad_hist_birch}
\caption{Construction of bespoke response functions for Norway birch. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_birch}
\end{figure}

\begin{figure*}[t]
  \includegraphics[width=12cm]{DO3SE_results_pody_gsto_o3}
  \caption{$\mathrm{POD_y}$ modeling results from $\mathrm{DO_3SE}$ model for three different PFTs over day of year (doy), March--October. A flux threshold $y=1\,\unit{nmol\,m^{-2}\,s^{-1}}$ per projected leaf area (PLA) has been chosen. \chem{[O_3]} are plotted on the same axis and scales as $G_\text{sto}^\text{leaf}$ but in units of $\unit{ppb}$. (a, b) Birch; (c, d) Norway spruce; (e, f) perennial grassland. From left to right: 2018, 2019. {\bf TODO: substitute with figure for Boreal PFTs?}}
  \label{fig:pody}
\end{figure*}

>>>>

%\graphicspath{{pictures/}}
\graphicspath{{figures/}}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{svanhovd_researchstation}\\
  %\includegraphics[width=8.3cm]{IMG_7739.JPG}
  \includegraphics[width=8.3cm]{fig01}
  \caption{NIBIO Environment Centre Svanhovd close by the settlement of Svanvik, Norway. (a) Atmospheric monitoring site and ozone garden have been marked. Aerial photography \copyright Norges Kartverk; (b) Clover in the Svanhovd ozone garden. The plants had to be secured against herbivores with a wire-mesh fence. The plants shown are approximately $6-12\,\unit{cm}$ in height.}
  \label{fig:svanhovd_research_station}
\end{figure}

@@

\begin{figure*}[t]
  %\includegraphics[width=12cm]{data_svanvik_2018_2019}
  \includegraphics[width=12cm]{fig02}
  \caption{Observational data from atmospheric monitoring at Svanhovd in 2018/19. The hatched areas indicate missing ozone monitoring data. (a) Hourly averaged ozone concentration; (b) hourly averaged temperature; (c) daily accumulated precipitation; (d) hourly averaged global irradiance.}
  \label{fig:data_svanvik_2018_2019}
\end{figure*}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{station_map_fennoscandia}
  \includegraphics[width=8.3cm]{fig03}
  \caption{Cap of the North. Locations of past and present ozone observation sites in northern Fennoscandia used within this study. For more details see Tab.~\ref{tab:ebas_obs}. The same color coding for each station as displayed herein will be used in all following figures.}
  \label{fig:station_map_fennoscandia}
\end{figure}

@@

\begin{figure*}[t]
  %\includegraphics[width=12cm]{ozone_timeseries_fenoscandic_obs.png}
  \includegraphics[width=12cm]{fig04}
  \caption{Time series of ozone observations in northern Fennoscandia (Tab.~\ref{tab:ebas_obs}). Data taken from EBAS. The hatched areas indicate time periods with insufficient quality control \citep{NILU2003}.}
  \label{fig:ozone_timesseries_fenoscandic_obs}
\end{figure*}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{climatediagram}
  \includegraphics[width=8.3cm]{fig05}
  \caption{Climate diagram following Walter and Lieth. The diagram is based on climatological data for Svanvik/Pasvik (1992--2012) downloaded from LandbruksMeteorologiske Tjeneste. Monthly averaged temperatures (red line) are displayed with standard error of mean as error band. Averaged monthly accumulated precipitation (blue bars) is shown with standard deviation of mean as error bars. Months with average temperatures below freezing are denoted with a star.}
  \label{fig:climatediagram}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_climatology_fenoscandic_obs_spline}
  \includegraphics[width=8.3cm]{fig06}
  \caption{Derivation of ozone climatologies. Density distributions are shown together with multi-annual mean of daily ozone concentrations \chem{[O_3]}. Splines have been fitted though daily mean \chem{[O_3]}. The climatology of daily mean ozone is shown together with $1\,\sigma$ standard deviation and standard error of the mean. Since \chem{[O_3]} are strongly correlated for sites at Jergul/Karasjok (NOR), Esrange (SWE), and Pallas (FIN) (see Fig.~\ref{fig:density_distribution}), data of these have been averaged together to derive a climatology for northern Fennoscandia. (a) Northern Fennoscandia; (b) Svanvik.}
  \label{fig:ozone_climatology_fenoscandic_obs_spline}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_climatologies_portrait}
  \includegraphics[width=8.3cm]{fig07}
  \caption{Comparison of climatologies derived from observational data (EBAS) with various ozone reanalysis products: (a) ECMWF: MACC reanalysis; (b) ECMWF: CAMS reanalysis; (c) Copernicus: Regional model reanalysis ensemble mean. As representative for the sites, the nearest neighboring grid point has been chosen. The ECMWF products do not reproduce observed surface ozone well. The MACC reanalysis is in general too low and displays an erroneous seasonal cycle. The CAMS reanalysis matches better but does not reproduce the seasonality in northern Fennoscandia. The ensemble mean of the Copernicus regional model reanalysis does reproduce the seasonal cycle in northern Fennoscandia, though the modeled ozone concentrations are slightly too low.}
  \label{fig:ozone_climatologies}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{temperature_signific_1}
  \includegraphics[width=8.3cm]{fig08}
  \caption{Temperature anomalies at Svanvik. Percentage of days warmer/colder than $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). The summer of 2018 was significantly warmer than average, especially May and July. The summer of 2019 was fairly average but significantly warmer than average in April and colder in July/August.}
  \label{fig:plot_temperature_anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{precipitation_signific_1}
  \includegraphics[width=8.3cm]{fig09}
  \caption{Precipitation anomalies at Svanvik. Percentage of days wetter/drier than $\pm \frac{1}{2}\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above $\pm\frac{1}{2}\,\sigma$ if a normal distribution is assumed ($30.8\,\unit{\%}$). Summer was significantly dry only in 2018, while fall was significantly dry in both years.}
  \label{fig:plot_precipitation_anomalies_svanvik}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{global_rad_signific_1}
  \includegraphics[width=8.3cm]{fig10}
  \caption{Global irradiance anomalies at Svanvik. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). In summer 2018 (May/July), global irradiance was significantly higher than on average, while 2019 had significantly less than normal irradiance in April/May and more in June.}
  \label{fig:global_rad_signific}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{ozone_signific_1}
  \includegraphics[width=8.3cm]{fig11}
  \caption{Ozone concentration anomalies at Svanvik. Ozone climatology has been corrected for an constant negative bias of $-1.2\,\unit{ppb}$. Percentage of days above/below $\pm 1\,\sigma$ from climatological mean displayed for each month. Negative deviations from climatology are shown as negative percentage. The annual positive/negative deviations are indicated in the respective corners (right upper/right lower). The hatched area between the dashed lines indicates the expected percentage of values falling above/below $\pm 1\,\sigma$ if a normal distribution is assumed ($15.9\,\unit{\%}$). July 2018 has not been corrected for the missing data due to data acquisition problems. The corrected value is indicated by the star (refer to Section~\ref{subsec:ozone_reco} for details). In April/May 2018, ozone was significantly higher than on average, while 2019 was generally an average year. In both years ozone concentrations were significantly below average in November.}
  \label{fig:ozone_signific}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_grassland}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_grassland}
  \includegraphics[width=8.3cm]{fig12}
\caption{Construction of bespoke response functions for grassland. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_grassland}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_func_opt_mean}
  \includegraphics[width=8.3cm]{fig13}
  \caption{Proposed metric to test bespoke response functions.}
  \label{fig:javis_func_opt_mean}
\end{figure}

@@

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{do3se_results_pod_v3_Birch}\\
  %\includegraphics[width=8.3cm]{do3se_results_pod_v3_Spruce}\\
  %\includegraphics[width=8.3cm]{do3se_results_pod_v3_Grassland}
  \includegraphics[width=8.3cm]{fig14}
  \caption{Comprehensive comparison of $\mathrm{DO_3SE}$ modeling results with default parameterization from mapping manual (MM)and bespoke parameters for Svanhovd. $\mathrm{POD_1}$ is shown for the different temperature (MM, boreal, cold) and light threshold (MM, PPFD0.8, PPFD1.2) parameterizations at the end of the MM GS (lighter colors and dotted lines) and a derived bespoke GS. (a) Birch; (b) Norway spruce; (c) Perennial grassland.}
  \label{fig:pody_rel}
\end{figure}

@@

%\videosupplement{TEXT} %% use this section when having video supplements available
\clearpage

@@

\appendixfigures  %% needs to be added in front of appendix figures
\begin{figure*}[t]
  \includegraphics[width=12cm]{figA1}
  \caption{Observed global irradiance at Svanvik. (a) Climatology (hourly maxima, mean, and minima); deviation from climatology (b) 2018; (c) 2019. The cyan lines indicate the $1\,\sigma$ level derived from climatology.}
  \label{fig:global_rad_clim}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{figA2}
  \caption{Probability densities and correlation coefficient for \chem{[O_3]} between different sites in northern Fennoscandia. Jergul/Karasjok is well correlated with Esrange, and Pallas. Svanvik displays highest correlation with Pallas. (a) Jergul/Karasjok--Esrange; (b) Jergul/Karasjok--Pallas; (c) Svanvik--Esrange; (d) Svanvik--Pallas.}
  \label{fig:density_distribution}
\end{figure*}

\begin{figure*}[t]
  \includegraphics[width=12cm]{figA3}
  \caption{Reconstruction of missing \chem{[O_3]} observation data at Svanvik in July 2018 based on derived hourly climatologies of northern Fennoscandia, Svanvik, and data Pallas. (a) Time series; (b) anomalies; (c) reconstruction.}
  \label{fig:ozone_reconstruction_2018_07}
\end{figure*}

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{figB1}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (doy) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure*}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_evergreen}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_evergreen}
  \includegraphics[width=12cm]{figB2}
\caption{Construction of bespoke response functions for Norway spruce. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_spruce}
\end{figure}

\begin{figure}[t]
  %\includegraphics[width=8.3cm]{javis_funcs_temp_hist_birch}\\
  %\includegraphics[width=8.3cm]{javis_funcs_rad_hist_birch}
  \includegraphics[width=12cm]{figB3}
\caption{Construction of bespoke response functions for Norway birch. (a) $f_\mathrm{T}$ and (b) $f_\mathrm{flight}$ are shown together with underlying $T_\mathrm{air}$ and $Q_0$ climatologies (probability density function - PDF), respectively. Original mapping manual parameterization is shown in comparison as solid line. Note that $Q_0$ has been truncated to $0.006$. PPFD0.8 and PPFD1.2 refer to $\alpha$ values increasing/decreasing PPFD at $f_\mathrm{light}=0.5$ by $\pm 20\,\%$, respectively.}
\label{fig:f_temp_birch}
\end{figure}

\begin{figure*}[t]
  \includegraphics[width=12cm]{figB4}
  \caption{$\mathrm{POD_y}$ modeling results from $\mathrm{DO_3SE}$ model for three different PFTs over day of year (doy), March--October. A flux threshold $y=1\,\unit{nmol\,m^{-2}\,s^{-1}}$ per projected leaf area (PLA) has been chosen. \chem{[O_3]} are plotted on the same axis and scales as $G_\text{sto}^\text{leaf}$ but in units of $\unit{ppb}$. (a, b) Birch; (c, d) Norway spruce; (e, f) perennial grassland. From left to right: 2018, 2019. {\bf TODO: substitute with figure for Boreal PFTs?}}
  \label{fig:pody}
\end{figure*}
